Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-07-14 draft.tex
rename section 2.2
move common knowledge statement to end of sec 2.2

\subsection{Interaction within a Period}
\label{sec:structure}

@@

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. There are an infinite number of discrete periods $t=1,2,\ldots$. Play proceeds in each period $t$ as follows until an absorbing state is reached.

@@

In order to fully describe the structure of the game, we next introduce the payoffs.

>>>>

\subsection{Details of the Dynamic Game}
\label{sec:structure}

@@

There are an infinite number of discrete periods $t=1,2,\ldots$. Play proceeds in each period $t$ as follows (and as shown in Figure 1) until an absorbing state is reached.

@@

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. We turn next to describing the payoffs.
